\documentclass[12pt]{article}
\usepackage[margin=0.5in]{geometry}
\pagestyle{empty}
\raggedright

\input{setup}

% Enable bold small caps: https://tex.stackexchange.com/a/386933
\usepackage{lmodern} % Switch to Latin Modern
\usepackage[T1]{fontenc}
\rmfamily
\DeclareFontShape{T1}{lmr}{b}{sc}{<->ssub*cmr/bx/sc}{}
\DeclareFontShape{T1}{lmr}{bx}{sc}{<->ssub*cmr/bx/sc}{}

\usepackage[dvipsnames]{xcolor}

\setlength{\tabcolsep}{0pt}
\usepackage{enumitem}
\setlist{leftmargin=*, noitemsep, topsep=0.25em}

\usepackage[hidelinks]{hyperref}
\urlstyle{same}

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}


\begin{document}

{\centering
  \textbox{\href{mailto:jjhan@vassar.edu}{jjhan@vassar.edu}}%
  \hfill {\huge \scshape {Jason Han}} \hfill%
  \textbox{\hfill \href{https://www.linkedin.com/in/jasonjhan/}
    {linkedin.com/in/jasonjhan}}\par
}

\vspace{-0.5em}
\hrulefill

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
  {\color{Red} \textbf{\textsc{Education}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
  \vspace{-1pt}
  \resumeheading{Vassar College}{May 2023}{B.A. Computer Science and Math}
    {Poughkeepsie, NY}
  \begin{itemize}
    \item Parallel Programming, Operating Systems, Compilers, Databases
    \item Multivariable Calculus, Linear Algebra, Probability
  \end{itemize}
\end{minipage}

\vspace{0.75em}
{\color{Red} \hrulefill}

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
  {\color{Red} \textbf{\textsc{Work\\Experience}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
  \resumeheading{IBM}{May 2022 -- Aug 2022}{Back End SDE Intern}{Boston, MA}
  \begin{itemize}
    \item Worked on the Watson Assistant Store team using JavaScript (Node.js),
      Kubernetes, and IBM Cloud.
    \item Created a weather bot using Watson Assistant and Watson Natural
      Language Understanding, hosted on IBM Code Engine.
    \item Improved validation of Actions conditions using Ajv schemas.
    \item Fixed failing Store end-to-end remote tests.
  \end{itemize}
  \vspace{0.5em}
  \resumeheading{Vassar URSI}{Jun 2021 -- Jul 2021}
    {Cognitive Science Researcher}{Poughkeepsie, NY}
  \begin{itemize}
    \item Validated the hypothesis that gene duplication and
      differentiation affects modularity and evolvability using
      artificial neural networks.
    \item Created a simulation program in Python and C++ using ROS 2 and Gazebo
      which simulates biological phenomenon such as genotype to phenotype
      mappings, neuron/sensor connectivity and weights, and fitness landscapes.
    \item Ran simulations in parallel using Python in Hopper, a
      high-performance computing cluster.
  \end{itemize}
  \vspace{0.5em}
  \resumeheading{Google, Inc.}{May 2020 -- Aug 2020}{STEP Intern}{Remote}
  \begin{itemize}
    \item Completed the entire web development process including writing design
      docs, implementation, unit testing, and deployment.
    \item Worked as a full-stack developer using Java Servlets, JavaScript,
      HTML, CSS, and JS frameworks.
    \item \textbf{Restaurant Roulette web app}:
    \begin{itemize}
      \item Used Google App Engine to deploy a web app that uses React and
        barba.js for the frontend.
      \item Created a backend using Java Servlets that implements a REST API
        to be used by the web app, and tested using JUnit and Mockito test
        suites.
      \item Integrated with Google Places API, Maps API, and OAuth API, as well
        as Google Datastore.
    \end{itemize}
  \end{itemize}
\end{minipage}

\vspace{0.75em}
{\color{Red} \hrulefill}

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
  {\color{Red} \textbf{\textsc{Leadership\\and\\Campus\\Activities}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
  \personalheading{VC++ Club}{President}{Feb 2020 -- Present}
  \personalheading{CS Majors Committee}{Vice President}{May 2022 -- Present}
  \personalheading{Teaching Assistant}{Compilers}{Aug 2022 -- Present}
  \personalheading{Teaching Assistant}{Operating Systems}{Jan 2022 -- May 2022}
  \phantom{why is this needed to prevent warnings?}
\end{minipage}

\vspace{0.75em}
{\color{Red} \hrulefill}

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
  {\color{Red} \textbf{\textsc{Skills}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
  \textbf{Languages}: JavaScript/HTML/CSS, Java, Python, C++, OCaml,
      SQL

  \textbf{Frameworks}: Node.js
  
  \textbf{Tools}: Git, Docker, Kubernetes
\end{minipage}

\end{document}
