\documentclass[12pt]{article}
\usepackage[margin=0.5in]{geometry}
\pagestyle{empty}
\raggedright

\input{setup}

% Enable bold small caps: https://tex.stackexchange.com/a/386933
\usepackage{lmodern} % Switch to Latin Modern
\usepackage[T1]{fontenc}
\rmfamily
\DeclareFontShape{T1}{lmr}{b}{sc}{<->ssub*cmr/bx/sc}{}
\DeclareFontShape{T1}{lmr}{bx}{sc}{<->ssub*cmr/bx/sc}{}

\usepackage[dvipsnames]{xcolor}

\setlength{\tabcolsep}{0pt}
\usepackage{enumitem}
\setlist{leftmargin=*, noitemsep, topsep=0.25em}

\usepackage[hidelinks]{hyperref}
\urlstyle{same}

\newcommand\textbox[1]{%
    \parbox{.333\textwidth}{#1}%
}


\begin{document}

{\centering
    {\huge \scshape {Jason Han}}
    \textbox{\href{mailto:jjhan@vassar.edu}
                  {jjhan@vassar.edu}\hfill}%
    \textbox{\hfil \small (347)-687-3687\hfil}%
    \textbox{\hfill \href{https://www.linkedin.com/in/jasonjhan/}
                         {linkedin.com/in/jasonjhan}}\par
}

\vspace{-0.5em}
\hrulefill

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
    {\color{Red} \textbf{\textsc{Education}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
    \vspace{-1pt}
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Vassar College} &
        {\small Poughkeepsie, NY}\\
        \textsl{\small B.A. Computer Science and Math} &
        {\small Expected: May 2023}
    \end{tabular*}
    \begin{itemize}
        \item Parallel Programming, Operating Systems, Compilers, Databases
        \item Multivariable Calculus, Linear Algebra, Probability
    \end{itemize}
\end{minipage}

\vspace{0.75em}
{\color{Red} \hrulefill}

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
    {\color{Red} \textbf{\textsc{Work\\Experience}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
    \resumeheading{IBM}{May 2022 -- Present}{Back End SDE Intern}
    \begin{itemize}
        \item Working on the Watson Assistant Store team using JavaScript
              (Node.js), Kubernetes, and IBM Cloud.
    \end{itemize}
    \vspace{0.5em}
    \resumeheading{Vassar Undergraduate Research Summer Institute (URSI)}
                  {June 2021 -- July 2021}{Cognitive Science Researcher}
    \begin{itemize}
        \item Validated the hypothesis that gene duplication and
              differentiation affects modularity and evolvability using
              artificial neural networks.
        \item Created a simulation program in Python and C++ using ROS 2 and
              Gazebo which
              simulates biological phenomenon such as genotype to phenotype
              mappings, neuron/sensor connectivity and weights, and fitness
              landscapes.
        \item Ran simulations in parallel using Python in Hopper, a high
              performance computing cluster.
    \end{itemize}
    \vspace{0.5em}
    \resumeheading{Google, Inc.}{May 2020 -- Aug 2020}{STEP Intern}
    \begin{itemize}
        \item Completed the entire web development process including writing
              design docs, implementation, unit testing, and deployment.
        \item Worked as a full-stack developer using Java Servlets, JavaScript,
              HTML, CSS, and JS frameworks.
        \item \textbf{Restaurant Roulette web app}:
        \begin{itemize}
            \item Used Google App Engine to deploy a web app that uses React
                  and barba.js for the frontend.
            \item Created a backend using Java Servlets that implements a
                  REST API to be used by the web app, and tested using JUnit
                  and Mockito test suites.
            \item Integrated with Google Places API, Maps API, and OAuth API,
                  as well as Google Datastore.
        \end{itemize}
    \end{itemize}
\end{minipage}

\vspace{0.75em}
{\color{Red} \hrulefill}

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
    {\color{Red} \textbf{\textsc{Leadership\\and\\Campus\\Activities}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
    \personalheading{VC++ Club}{President}{Feb 2020 -- Present}
    \personalheading{CS Majors Committee}{Vice President}{May 2022 -- Present}
    \personalheading{Teaching Assistant}{Compilers}{August 2022 -- Present}
    \personalheading{Teaching Assistant}{Operating Systems}{Jan 2022 -- May 2022}
    \phantom{why is this needed to prevent warnings?}
\end{minipage}

\vspace{0.75em}
{\color{Red} \hrulefill}

\begin{minipage}[t]{0.15\textwidth}\vspace{-0.5em}%
    {\color{Red} \textbf{\textsc{Skills}}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.82\textwidth}\vspace{-0.5em}%
    \begin{itemize}
        \item \textbf{Languages}: JavaScript/HTML/CSS, Java, Python, C++, OCaml, SQL
        \item \textbf{Frameworks}: Node.js
        \item \textbf{Tools}: Git, Kubernetes, Docker
    \end{itemize}
\end{minipage}

\end{document}
